An inventory of human light exposure related behaviour

### 2023-12-04 manuscript_SciRep.Rmd
Figure 6 space adjusted

F5.tic <- ggplot(F5.test.data, aes(x=Theta, y=F5.T1)) +
  geom_line()+apatheme_3+
  labs(y="Test Information", title="F5:Using light in the morning and during daytime") +ylim(0,8)+geom_area()+aes(fill= "#B09C8599")+theme(legend.position="none")+
scale_fill_identity()+xlab(expression(theta)) + 
  ylab(expression(I(theta)))

>>>>

F5.tic <- ggplot(F5.test.data, aes(x=Theta, y=F5.T1)) +
  geom_line()+apatheme_3+
  labs(y="Test Information", title="F5: Using light in the morning and during daytime") +ylim(0,8)+geom_area()+aes(fill= "#B09C8599")+theme(legend.position="none")+
scale_fill_identity()+xlab(expression(theta)) + 
  ylab(expression(I(theta)))
